Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-07-17 ms.qmd
Adding note about how to also modify individual variation in performance (i.e height of curves)

# Simulation 1. Assume optimum is rather constant among individuals 
#parameters
delta =  35  
sigma =  9 + rnorm(n, 0, ind_sd)
alpha = -15 + rnorm(n, 0, ind_sd)

>>>>

# Simulation 1. Assume optimum is rather constant among individuals 
#parameters
delta =  35  
sigma =  9 + rnorm(n, 0, ind_sd)
alpha = -15 + rnorm(n, 0, ind_sd)
# k=2 # note that, if we want to control the between individual differences in performance we can multiply curve by constant. Can do that and add variation and then all aspects of the curve can be modified.
